Physics of Tidal Dissipation in Early-Type Stars and White Dwarfs: Hydrodynamical Simulations of Internal Gravity Wave Breaking in Stellar Envelopes

### 2020-02-21 writeups/Su_IGW_break.tex

    \includegraphics[width=0.45\textwidth]{plots/yubo_000134_labeled.png}\hfil
    %
    \includegraphics[width=0.45\textwidth]{plots/yubo_000451_labeled.png}
    \caption{Snapshots of $u_x$ and $\Upsilon$ in the fiducial simulation
    illustrating distinct phases of the evolution of the flow. Damping layers
    are shaded in light grey (see Section~\ref{ss:damping}), while the forcing
    zone (see Section~\ref{ss:forcing}) is shaded in light green (boundaries are
    at $z_0 \pm 3\sigma$). The four panels illustrate (i) the initial transient
    wave breaking phase, (ii) formation of a distinct critical layer, (iii)
    steepening of the critical layer, and (iv) downward advance of the critical
    layer.}\label{fig:snapshots}
\end{figure*}

@@

This result suggests that the critical layer width is regulated by the
competition between steepening induced by IGW breaking and broadening due to
shear instability. This width does not vary significantly with resolution in our
resolved simulations (see Fig.~\ref{fig:agg}). $\mathrm{Ri} \sim 0.5$ can be
used to calculate the critical layer width in stars, where $N^2$ and
$\overline{U}_c$ (corresponding to the tidal frequency) are known.
\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{plots/nl_f_ri.png}
    \caption{Local Richardson number (Eq.~\eqref{eq:ri_med_def}) of the flow at
    the critical layer over time (in units of $N^{-1}$) in our fiducial
    simulation. The red and solid green lines denote respectively the minimum
    and median of $\mathrm{Ri}_x(x, t)$. These numbers measure the mean and
    spread in width of the critical layer over $x$. Note that $\mathrm{Ri} \sim
    \frac{1}{4}$ corresponds to the KHI, so this plot suggests the shear at the
    critical layer does not steepen past the onset of the
    KHI.}\label{fig:nl_f_ri}
\end{figure}

>>>>

    \includegraphics[width=0.45\textwidth]{plots/yubo_000134_labeled.png}\hfil
    %
    \includegraphics[width=0.45\textwidth]{plots/yubo_000451_labeled.png}
    \caption{Snapshots of $u_x$ and $\Upsilon \equiv \ln \p{\rho / \bar{\rho}}$
    in the fiducial simulation illustrating distinct phases of the evolution of
    the flow. Damping layers are shaded in light grey (see
    Section~\ref{ss:damping}), while the forcing zone (see
    Section~\ref{ss:forcing}) is shaded in light green (boundaries are at $z_0
    \pm 3\sigma$). The four panels illustrate (i) the initial transient wave
    breaking phase, (ii) formation of a distinct critical layer, (iii)
    steepening of the critical layer, and (iv) downward advance of the critical
    layer.}\label{fig:snapshots}
\end{figure*}

@@

This result suggests that the critical layer width is regulated by the
competition between steepening induced by IGW breaking and broadening due to
shear instability. This width does not vary significantly with resolution in our
resolved simulations (see Fig.~\ref{fig:agg}). As such, $\mathrm{Ri} \sim 0.5$
can be used to calculate the critical layer width in stars, where $N^2$ and
$\overline{U}_c$ (corresponding to the tidal frequency) are known.
\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{plots/nl_f_ri.png}
    \caption{Local Richardson number (Eq.~\eqref{eq:ri_med_def}) of the flow at
    the critical layer over time (in units of $N^{-1}$) in our fiducial
    simulation. The red and solid green lines denote respectively the minimum
    and median of $\mathrm{Ri}_x(x, t)$. These numbers measure the mean and
    spread in width of the critical layer over $x$. Note that $\mathrm{Ri} \sim
    \frac{1}{4}$ corresponds to the KHI, so this plot suggests the shear at the
    critical layer does not steepen past the onset of the
    KHI.}\label{fig:nl_f_ri}
\end{figure}
